%-------------------------
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
    \textbf{\Huge \scshape Vivek Kumar Singh} \\ \vspace{1pt}
    \small 7054015768 $|$ \href{mailto:x@x.com}{\underline{vschs007@gmail.com}} $|$ 
    %\href{https://linkedin.com/in/...}{\underline{linkedin.com/in/jake}} $|$
   % \href{https://github.com/...}{\underline{github.com/jake}}
\end{center}

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C, C\#, SQL , HTML/CSS} \\
     \textbf{Areas of Interest}{: Development, Databases, Big Data, ML/AI} \\
     \textbf{Frameworks}{: MSSQL, MYSQL, Flask, Jira, Agile Development,Wordpress} \\
     \textbf{Developer Tools}{: Git, AWS , Visual Studio, PyCharm, Eclipse , Anaconda Navigator} \\
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib, OpenCV}
    }}
 \end{itemize}




%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Associate Software Engineer , Globallogic India}{October 2019 -- Present}
      {Associate Software Engineer}{}
      \resumeItemListStart
        \resumeItem{Development of new features for Fintech and Insurance Management.}
        \resumeItem{Working on VB.NET and REST API to control the behavior and functionalities of different modules. }
        
      \resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{http://knit.ac.in}{\underline{Kamla Nehru Institute of Technology , Sultanpur}}}{B.Tech}
      {Information Technology (77.82\%)}{2019}
    \resumeSubheading
      {\href{https://en.wikipedia.org/wiki/Central_Hindu_Boys_School}{\underline{Central Hindu Boys School SSS BHU, Varanasi}}}{Secondary School}
      {CBSE (88.40\%)}{2014}
     \resumeSubheading
      {\href{https://en.wikipedia.org/wiki/Central_Hindu_Boys_School}{\underline{Central Hindu Boys School SSS BHU, Varanasi}}}{High School}
      {CBSE (10.0 CGPA)}{2012}
  \resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://github.com/vschs007/flask-realtime-face-detection-opencv-python}{\textbf{\underline{\large Realtime Face Recognition System}}}}{}
          
          \resumeItemListStart
            \resumeItem
            {Used Flask microframework  to deploy the App}
            \resumeItem{Use of OpenCV Library.}
            \resumeItem{Used Haar Cascade Classifiers for face detection}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\large Driver Drowsiness Detection and Alarming System}}{}
          
          \resumeItemListStart
            \resumeItem{Developed a Model to detect drownsiness or distraction from road.}
            \resumeItem{Deployed the model on a rasberry pi in order to supply it as a module to the vendors.}
            
          \resumeItemListEnd
     \resumeProjectHeading
          {\textbf{\large ProjectWala}}{}
          
          \resumeItemListStart
            \resumeItem{Built a Platform on PHP to accept the project requests of students.}
            \resumeItem{Worked mainly on delivering the working projects along with documentation.}
            
          \resumeItemListEnd
     \resumeProjectHeading
      {\href{https://play.google.com/store/apps/details?id=com.googl.sample.cloudvision}{\textbf{\underline{\large CloudVision Smart AI assistant}}}}{}
     
         \resumeItemListStart
         \\
           \resumeItem{Used Google CloudVision API to create an Android app to identify the objects in Images.}
         \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Trainings/Courses}
\resumeSubHeadingListStart
\resumeProjectHeading
  {\textbf{\large Emerging Trends in Computer Science}}{MNNIT,Allahabad}
  
  \resumeItemListStart
  \resumeItem{This course was focused on exposing students to modern technologies such as IoT , Big data ,Machine Learning and SDN.}
  \resumeItemListEnd
  \resumeSubheading
      {\href{https://www.coursera.org/account/accomplishments/certificate/ZE9PD6QJ2Z7E}{\underline{Introduction to Big Data}}}{COURSERA}
      {University of California, San Diego (93.9\%)}
      
    \resumeSubheading
      {\href{https://www.coursera.org/account/accomplishments/certificate/NE2Y3BSKW5FY}{\underline{Getting Started with Python }}}{COURSERA}
      {University of Michigan (95.8\%)}{}

  
\section{Awards/Achievements}
\resumeItemListStart
\resumeItem{\large Honorable mentions on PayPal’s Wall of Fame , July 2017 for submitting a bug report  under PayPal’s Bug Hunter Program.
}
\resumeItem{\large Successfully reporting a bug to Netflix.}
\resumeItem{\large Bug finding on Disney-Hotstar and reporting.}
\resumeItem{\large 3rd Position in GL-Sparks 30Hacks - Globallogic India Pvt Ltd.}
\resumeItem{\large Open Source Contribution to PayPal’s Accessible HTML5 Video Player, Google playhvz Repository.
}
\resumeItem{\large Published Multiple Amazon Alexa Skills}
\resumeItem{\large Published Google Assistant Skills.}
\resumeItem{\large AIR NCC  ‘A’ Certificate with ‘AYE’ grade ( 2011-2012)}
\resumeItem{\large Certification of Merit From CBSE (2012), For securing perfect 10.0 CGPA in all subjects in Class X.}
\resumeItem{\large Best Cadet Award at Combined Annual Training Camp ( CATC) ,2011  held at BHU, Varanasi , among 400 Cadets.}

\section{Hobbies}
\resumeItem{\large Watching Documentaries}
\resumeItem{\large Pentesting , Blogging.}

%-------------------------------------------
\end{document}
